### 2016-06-10 Paper_v4.tex
Updates

We tested the predictive power of the reduced order complement model with data not used during model training (Fig. \ref{fig-prediction}).
Six validation cases were considered, three for C3a and C5a, respectively.
All model parameters and initial conditions were fixed for the validation simulations (with the exception of zymosan).
The ensemble of reduced order models predicted the qualitative dynamics of C3a formation (Fig. \ref{fig-prediction}, left column),
and C5a formation (Fig. \ref{fig-prediction}, right column) at three inducer concentrations.
However, there were shortcomings with model performance, especially for the C3a prediction.
First, while the overall C3a trend was captured, the level of C3a was consistently under-predicted (outside of our 99\% confidence interval) in all cases (Fig. \ref{fig-prediction}, left column).
We believe the C3a under-prediction was related to our choice of training data, and how we modeled C4BP interactions.
We trained the model using 1g zymosan, but predicted cases with much less initiator.
Next, the C4BP interactions were modeled as irreversible binding steps resulting in completely inactive complexes.
However, the binding of C4BP with complement proteins is likely reversible, and CP C3 convertase may have residual activity even in the bound form.
Thus, the model likely over-predicted the influence of C4BP.
Second, while the C5a measurements were within the 99\% confidence estimate, we failed to capture the concave down curvature for the 0.001g and 0.01g zymosan cases.
The decreasing slope of the C5a may indicate cofactor limitation, or missing biology which we have not accounted for in the reduced order approach.
Despite these shortcomings, we qualitatively predicted unseen experimental data, including correctly capturing the dynamic time scale of C3a formation,
and the correct order of magnitude for the concentration of C5a for three inducer levels.
Next, we used global sensitivity and robustness analysis to determine which parameters and species controlled the performance of the complement model.

@@

\subsection*{Global analysis of the reduced order complement model.}
We conducted sensitivity analysis to estimate which parameters controlled the performance of the reduced order complement model.
We calculated the sensitivity of the C3a and C5a residuals to changes in model parameters with and without zymosan for the ensemble of parameter sets (Fig. \ref{fig-SA}A - D).
In the absence of zymosan (where only the alternative pathway is active), $k_{f,C3b}$ (tickover formation of C3b) and $k_{d,C3a}$ (rate constant governing C3a degradation)
controlled the C3a fit (Fig. \ref{fig-SA}A). Interestingly, neither $k_{c,C3C,AP}$ (the rate constant governing AP C3-convertase activity) nor $k_{f,C3C,AP}$ (the rate constant governing AP C3-convertase formation) were sensitive in the absence of zymosan.
Thus, C3a formation in the alternative pathway was more heavily influenced by the spontaneous hydrolysis of C3, rather than AP C3-convertase activity, in the absence of zymosan.
On the other hand, the C5a residual was strongly sensitive to tickover parameters e.g., $k_{f,C3b}$, and to a lesser extent $k_{f,C3C,AP}$ as well as
parameters controlling AP C5 convertase activity in the absence of zymosan (Fig. \ref{fig-SA}B).
Thus, AP C3-convertase did not influence C3a dynamics, but strongly effected C5a formation in the absence of zymosan.
In the presence of zymosan, the C3a residual was controlled by the formation and activity of the CP C3 convertase, as well as tickover and degradation parameters (Fig. \ref{fig-SA}C).
Further, the C5a residual was influenced by lectin initiation parameters, the formation and activity of CP C5 convertase, and the inhibition by C4BP in the presence of zymosan (Fig. \ref{fig-SA}D).
Globally, sensitivity analysis suggested that lectin pathway parameters dominated system performance in the presence of zymosan, and that C5a formation was sensitive to both
C3 and C5 convertase activity, while C3a was robust to the AP C3 convertase.
In the absence of zymosan, the tickover parameters were important to both C3a and C5a formation, but C5a was also sensitive to both AP C3 and C5 convertase activity.
We compared the sensitivity results to current therapeutic approaches; pathways involving sensitive parameters have been targeted for clinical intervention (Fig. \ref{fig-SA}E).
Thus, there was a qualitative overlap between sensitivity and the potential of biochemical efficacy.
However, sensitivity coefficients are only a local measure of how small changes in a parameter value affects model performance.
To more closely simulate a clinical intervention e.g., administration of an anti-complement inhibitor, we performed
robustness analysis on the model ensemble.

>>>>

We tested the predictive power of the reduced order complement model with data not used during model training (Fig. \ref{fig-prediction}).
Six validation cases were considered, three for C3a and C5a, respectively.
All model parameters and initial conditions were fixed for the validation simulations (with the exception of zymosan).
The ensemble of reduced order models predicted the qualitative dynamics of C3a formation (Fig. \ref{fig-prediction}, left column),
and C5a formation (Fig. \ref{fig-prediction}, right column) at three inducer concentrations.
However, there were shortcomings with model performance, especially for the C3a prediction.
First, while the overall C3a trend was captured, the level of C3a was consistently under-predicted (outside of our 99\% confidence interval) in all cases (Fig. \ref{fig-prediction}, left column).
We believe the C3a under-prediction was related to our choice of training data, and how we modeled C4BP interactions.
We trained the model using 1g zymosan, but predicted cases with much less initiator.
Next, the C4BP interactions were modeled as irreversible binding steps resulting in completely inactive complexes.
However, the binding of C4BP with complement proteins is likely reversible, and CP C3 convertase may have residual activity even in the bound form.
Thus, the model likely over-predicted the influence of C4BP.
Second, while the C5a measurements were within the 99\% confidence estimate, we failed to capture the concave down curvature for the 0.001g and 0.01g zymosan cases.
The decreasing slope of the C5a may indicate cofactor limitation, or missing biology which we have not accounted for in the reduced order approach.
Despite these shortcomings, we qualitatively predicted unseen experimental data, including correctly capturing the time scale of C3a formation,
and the correct order of magnitude for C5a for three inducer levels.
Next, we used global sensitivity and robustness analysis to determine which parameters and species controlled the performance of the complement model.

@@

\subsection*{Global analysis of the reduced order complement model.}
We conducted sensitivity analysis to estimate which parameters controlled the performance of the reduced order complement model.
We calculated the sensitivity of the C3a and C5a residuals to changes in model parameters with and without zymosan for the ensemble of parameter sets (Fig. \ref{fig-SA}A - D).
In the absence of zymosan (where only the alternative pathway is active), $k_{f,C3b}$ (tickover formation of C3b) and $k_{d,C3a}$ (rate constant governing C3a degradation)
controlled the C3a fit (Fig. \ref{fig-SA}A). Interestingly, neither $k_{c,C3C,AP}$ (the rate constant governing AP C3-convertase activity) nor $k_{f,C3C,AP}$ (the rate constant governing AP C3-convertase formation) were sensitive in the absence of zymosan.
Thus, C3a formation in the alternative pathway was more heavily influenced by the spontaneous hydrolysis of C3, rather than AP C3-convertase activity, in the absence of zymosan.
On the other hand, the C5a residual was strongly sensitive to tickover parameters e.g., $k_{f,C3b}$, and to a lesser extent $k_{f,C3C,AP}$ as well as
parameters controlling AP C5 convertase activity in the absence of zymosan (Fig. \ref{fig-SA}B).
Thus, AP C3-convertase did not influence C3a dynamics, but strongly effected C5a formation in the absence of zymosan.
In the presence of zymosan, the C3a residual was controlled by the formation and activity of the CP C3 convertase, as well as tickover and degradation parameters (Fig. \ref{fig-SA}C).
Further, the C5a residual was influenced by lectin initiation parameters, the formation and activity of CP C5 convertase, and the inhibition by C4BP in the presence of zymosan (Fig. \ref{fig-SA}D).
Globally, sensitivity analysis suggested that lectin pathway parameters dominated system performance in the presence of zymosan, and that C5a formation was sensitive to both
C3 and C5 convertase activity, while C3a was robust to the AP C3 convertase.
In the absence of zymosan, the tickover parameters were important to both C3a and C5a formation, but C5a was also sensitive to both AP C3 and C5 convertase formation.
We compared the sensitivity results to current therapeutic approaches; pathways involving sensitive parameters have been targeted for clinical intervention (Fig. \ref{fig-SA}E).
Thus, there was a qualitative overlap between sensitivity and the potential of biochemical efficacy.
However, sensitivity coefficients are only a local measure of how small changes in a parameters affect model performance.
To more closely simulate a clinical intervention e.g., administration of an anti-complement inhibitor, we performed
robustness analysis.
